R for Clinical Study Reports and Submission

### 2021-11-06 submission-package.Rmd
rename `adam_data/` as `data-adam/`

You can then proceed to move the file `r0pkgs.txt` to the folder
`ectddemo/m5/datasets/ectddemo/analysis/adam/programs`,
or specify the output text file path above directly.

@@

Besides the R packages, we need to convert the R Markdown (`.Rmd`) files
into `.txt` files and saved them in the `programs` folder.
You can do this with `knitr::purl()`:

>>>>

You can then proceed to move the file `r0pkgs.txt` to the folder
`ectddemo/m5/datasets/ectddemo/analysis/adam/programs/`,
or specify the output text file path above directly.

@@

Besides the R packages, we need to convert the R Markdown (`.Rmd`) files
into `.txt` files and saved them in the `programs/` folder.
You can do this with `knitr::purl()`:

### 2021-11-06 tlf-ae-summary.Rmd
fix grammar, trailing spaces, file organization
rename `adam_data/` as `data-adam/`

```{r}
adsl <- read_sas("adam_data/adsl.sas7bdat")
adae <- read_sas("adam_data/adae.sas7bdat")
```

@@

The procedure to generate a AE summary table can be summarized as follow：

>>>>

```{r}
adsl <- read_sas("data-adam/adsl.sas7bdat")
adae <- read_sas("data-adam/adae.sas7bdat")
```

@@

The procedure to generate an AE summary table can be summarized as follow:

### 2021-11-06 tlf-efficacy.Rmd
Update tlf-efficacy.Rmd
rename `adam_data/` as `data-adam/`

```{r}
adsl <- read_sas("adam_data/adsl.sas7bdat")
adlb <- read_sas("adam_data/adlbc.sas7bdat")
```

@@

- Step 1: Read the data into R, i.e., `adsl` and `adlb`.
- Step 2: Define the analysis dataset. In this example, we define two analysis datasets. The first dataset is the efficacy population (`gluc`). The second dataset is the collection of all records post baseline and on or before week 24 (`ana`).
- Step 3: Impute the missing values. In our example, we name the `ana` dataset after imputation as `ana_locf`.
- Step 4: Summarize `gluc`, i.e., calculate the mean and standard derivation, and then format it into an RTF table.
- Step 5: Summarize `ana_locf`, i.e., calculate the pairwise comparison by ANCOVA model, and then format it into an RTF table.
- Step 6: Set the results from Step 4 and Step 5 and output.

>>>>

```{r}
adsl <- read_sas("data-adam/adsl.sas7bdat")
adlb <- read_sas("data-adam/adlbc.sas7bdat")
```

@@

- Step 1: Read the data into R, i.e., `adsl` and `adlb`.
- Step 2: Define the analysis dataset. In this example, we define two analysis datasets. The first dataset is the efficacy population (`gluc`). The second dataset is the collection of all records post baseline and on or before week 24 (`ana`).
- Step 3: Impute the missing values. In our example, we name the `ana` dataset after imputation as `ana_locf`.
- Step 4: Summarize `gluc`, i.e., calculate the mean and standard derivation, and then format it into an RTF table.
- Step 5: Summarize `ana_locf`, i.e., calculate the pairwise comparison by ANCOVA model, and then format it into an RTF table.
- Step 6: Combine the outputs in step 4 and step 5 by rows.
